Modelling the Retinotectal projection - can competition provide a stopping mechanism?

### 2020-03-24 paper/notes.tex
Some recent notes on different manipulations for the models

@@

$\xi_\gamma$ is drawn from a normal distribution with mean 0 and standard
deviation $\sigma_\rho$.
%
% BIBLIOGRAPHY
%
\selectlanguage{English}
\bibliographystyle{abbrvnotitle}
\bibliography{RetinoTectal}

>>>>

% Nice quotes
\usepackage{csquotes}

@@

$\xi_\gamma$ is drawn from a normal distribution with mean 0 and standard
deviation $\sigma_\rho$.

\section{Results}

\subsection{Wild type}

The operation of the model without modifiction and with zero or low noise.

\subsection{Manipulations}

Reference \cite{goodhill_development_2005} (from which the headings and quotes
below are taken) gives a list of features which a model of retinotectal
development or regeneration should address.

\subsubsection{Ectopic targeting}

\begin{displayquote}
\emph{Retinal axons entering the tectum via abnormal trajectories can still find
their appropriate termination sites (Finlay et al. 1979b; Harris 1982,
1984). This suggests the presence of vector signals throughout the tectum
pointing axons towards their correct termination sites.}
\end{displayquote}

The orthogonal gradients in the current model which signal growth direction of
axonal growth cones naturally provide the vector signals which ensure that
regardless of entry point, growth cones tend towards their correct location.

\subsubsection{Shifting connections}

\begin{displayquote}
\emph{In some fish and amphibians, the retina grows by addition of new neurons
around the ciliary margin, while the tectum grows by addition of cells to its
caudomedial edge (Gaze et al. 1974; Fraser 1983).The retinotectal map remains
ordered throughout this time, indicating that the retinotectal projection is
continually shifting caudally. This suggests that, at least in these species,
either chemoaffinity gradients do not irreversibly specify the map or the
gradients must evolve with time.}
\end{displayquote}

The current model should work under the condition that the underlying domain
is increased in size, with the competition acting to ensure that the entire
domain is filled and the ordering maintained.

\subsubsection{Rotation experiments}

\begin{displayquote}
\emph{If a Xenopus presumptive tectum is rotated early enough during devel- opment,
a map is formed that is normal relative to the whole animal, whereas later
rotations lead to a rotated map (Chung \& Cooke 1978).}
\end{displayquote}

\subsubsection{Map compression and expansion}

\begin{displayquote}
\emph{The map formed after removal of half the retina initially covers half the
tectum (Attardi \& Sperry 1963), but then gradually expands to fill the whole
tectum (Schmidt et al. 1978). The axon terminal density remains the same
(Schmidt et al.  1978). If the optic nerve is then made to regenerate again,
an expanded map is immediately formed (Schmidt 1978). If half the tectum is
ablated, the regenerated map is compressed into the remaining tectal space
(Yoon 1971; Sharma 1972; Cook 1979; Finlay et al. 1979a).}
\end{displayquote}

\subsubsection{Translocation}

\begin{displayquote}
\emph{A}
\end{displayquote}

\subsubsection{Compound-eye experiments}

\begin{displayquote}
\emph{B}
\end{displayquote}

%
% BIBLIOGRAPHY
%
\selectlanguage{English}
\bibliographystyle{abbrvnotitle}
\bibliography{RetinoTectal}
